---
title: "PACBOARD report"
output: word_document
params:
  person: NA
  df_pacboard: NULL
  cost_variables: ""
  utility_variables: ""
  disutility_variables: ""
  probability_variables: ""
  relative_effectiveness_variables: ""
  intervention_total_discounted_qalys: ""
  intervention_total_discounted_costs: ""
  comparator_total_discounted_qalys: ""
  comparator_total_discounted_costs: ""
  intervention_total_undiscounted_qalys: ""
  intervention_total_undiscounted_costs: ""
  comparator_total_undiscounted_qalys: ""
  comparator_total_undiscounted_costs: ""
  summary_stats: TRUE
  corr_matrix: TRUE
  validation_checks_choice: TRUE
  ce_plot_choice: TRUE
  ice_plot_choice: TRUE
  ice_summary_choice: TRUE
  ceac_plot_choice: TRUE
  col_ice: ""
  n_it_highlight: NULL
  wtp_ice: NULL
  ceac_min: 0 
  ceac_max: 100000
  ceac_step: 5000
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
require(pacheck)
require(dplyr)
require(tidyr)
require(ggplot2)
require(purrr)
require(magrittr)
```

# Introduction
This report has been generated on `r Sys.Date()``r ifelse(params$person != '', paste0(" by ", params$person, "."), ".")`  

`r if(params$summary_stats == TRUE) {paste("# Summary uploaded data")}`
```{r summ}
if(is.data.frame(params$df_pacboard)) {
  if(params$summary_stats == TRUE) {
    variables <- c(
      params$cost_variables,
      params$utility_variables,
      params$disutility_variables,
      params$probability_variables,
      params$relative_effectiveness_variables,
      params$intervention_total_discounted_qalys,
      params$intervention_total_discounted_costs,
      params$comparator_total_discounted_qalys,
      params$comparator_total_discounted_costs
    )
    variables <- variables[which(variables != "")] # selection of variables for summary stats depending on non-empty selection
    
    if(length(variables) < 1) {
      paste0("There are no variables selected.")
    } else {    
      knitr::kable(
        as.data.frame(
          pacheck::generate_sum_stats(params$df_pacboard %>%
                                        dplyr::select(!!!variables))
        ))
      }
    }
} else {
    print("No data has been uploaded to PACBOARD.")
  }
```

`r if(params$corr_matrix == TRUE) {paste("# Correlation matrix")}`
```{r corr}
if(is.data.frame(params$df_pacboard)) {
  if(params$corr_matrix == TRUE) {
     invalid_cols_non_numeric <- params$df_pacboard %>%
      dplyr::select(where( ~ !is.numeric(.x))) %>%
      names()
    
    invalid_cols_no_variance <- params$df_pacboard %>%
      dplyr::select(-any_of(invalid_cols_non_numeric)) %>%
      dplyr::select(where( ~ var(.x, na.rm = TRUE) <= 1e-4)) %>%
      names()
    
    valid_data <- params$df_pacboard %>%
      dplyr::select(-any_of(invalid_cols_non_numeric),
                    -any_of(invalid_cols_no_variance))
    
    correlations <- valid_data %>%
      cor(use = "pair") %>%
      as_tibble(rownames = "x") %>%
      tidyr::pivot_longer(-x, names_to = "y", values_to = "cor") %>%
      mutate(
        x = factor(x, names(valid_data)),
        y = factor(y, names(valid_data) %>% rev())
      )
    plot_cor <- correlations %>%
      ggplot(aes(x, y, fill = cor)) +
      geom_raster() +
      scale_fill_continuous(limits = c(min(correlations$cor, 0), max(correlations$cor, 1))) +
      theme(axis.text.x = element_text(angle = 45),
            axis.title = element_blank())
    plot_cor
  }
}
```


`r if(params$validation_checks_choice == TRUE) {paste("# Validation checks")}`

`r if(params$validation_checks_choice == TRUE & params$probability_variables %>% length()) {paste("## Probabilities")}`
```{r validation_probs, warning = FALSE}
if(params$validation_checks_choice == TRUE &
   params$probability_variables %>% length()) {
  valid_probs_pos <- pacheck::do_check(
    params$df_pacboard,
    params$probability_variables,
    ~ .x >= 0,
    "positive",
    "all probabilities are {label_check}"
  )
  valid_probs_lt1 <- pacheck::do_check(
    params$df_pacboard,
    params$probability_variables,
    ~ .x <= 1,
    "lower or equal to 1",
    "all probabilities are {label_check}"
  )
  
   msg_probs <- paste(valid_probs_pos$messages$message,
                      valid_probs_lt1$messages$message,
                      sep = "\n"
                      )
   cat(msg_probs)
}
```

`r if(params$validation_checks_choice == TRUE & params$utility_variables %>% length()) {paste("## Utilities")}`
```{r validation_utils, warning = FALSE}
if(params$validation_checks_choice == TRUE &
   params$utility_variables %>% length()) {
  valid_utils_pos <- pacheck::do_check(
    params$df_pacboard,
    params$utility_variables,
    ~ .x >= 0,
    "positive",
    "all utility values are {label_check}"
  )
  valid_utils_lt1 <- pacheck::do_check(
    params$df_pacboard,
    params$utility_variables,
    ~ .x <= 1,
    "lower or equal to 1",
    "all utility values are {label_check}"
  )
  
  msg_utils <- paste(valid_utils_pos$messages$message,
                     valid_utils_lt1$messages$message,
                     sep = "\n"
                     )
  cat(msg_utils)
}
```

`r if(params$validation_checks_choice == TRUE & params$disutility_variables %>% length()) {paste("## Disutilities")}`
```{r validation_disutils, warning = FALSE}
if(params$validation_checks_choice == TRUE &
   params$disutility_variables %>% length()) {
  valid_disutils_neg <- pacheck::do_check(
    params$df_pacboard,
    params$disutility_variables,
    ~ .x < 0,
    "negative",
    "all disutility values are {label_check}"
  )
  valid_disutils_neg$messages$message
  }
```

`r if(params$validation_checks_choice == TRUE & params$cost_variables %>% length()) {paste("## Costs")}`
```{r validation_costs, warning = FALSE}
if(params$validation_checks_choice == TRUE &
   params$cost_variables %>% length()) {
  valid_costs <- pacheck::do_check(params$df_pacboard,
                                   params$cost_variables,
                                   ~.x >= 0,
                                   "positive",
                                   "all costs are {label_check}")
  valid_costs$messages$message
}
```

`r if(params$validation_checks_choice == TRUE & params$relative_effectiveness_variables %>% length()) {paste("## Relative effectiveness")}`
```{r validation_relative_effectiveness, warning = FALSE}
if(params$validation_checks_choice == TRUE &
   params$relative_effectiveness_variables %>% length()) {
  valid_relative_effectiveness <- pacheck::do_check(
    params$df_pacboard,
    params$relative_effectiveness_variables,
    ~ .x >= 0,
    "positive",
    "all relative effectiveness values are {label_check}"
  )
  valid_relative_effectiveness$messages$message
}
```

`r if(params$validation_checks_choice == TRUE & params$intervention_total_discounted_qalys != "" & params$comparator_total_discounted_qalys != "") {paste("## Outcomes: total discounted QALYs")}`
```{r validation_t_qalys, warning = FALSE}
msg_qalys <- c()
if(params$validation_checks_choice == TRUE &
   params$intervention_total_discounted_qalys != "" &
   params$comparator_total_discounted_qalys != "") {
  valid_qalys_int <- pacheck:::do_check(
    params$df_pacboard,
    params$intervention_total_discounted_qalys,
    ~ .x > 0,
    "positive",
    "total discounted QALYs are {label_check} for the intervention"
  )
  valid_qalys_comp <- pacheck:::do_check(
    params$df_pacboard,
    params$comparator_total_discounted_qalys,
    ~ .x > 0,
    "positive",
    "total discounted QALYs are {label_check} for the comparator"
  )
  
  msg_qalys <- paste(valid_qalys_int$messages$message,
                     valid_qalys_comp$messages$message,
                     sep = "\n")
}
if(params$validation_checks_choice == TRUE &
   params$intervention_total_discounted_qalys != "" &
   params$intervention_total_undiscounted_qalys != "") {
  valid_disc_qalys_int <- pacheck:::do_check(
        params$df_pacboard,
        params$intervention_total_discounted_qalys,
        ~ .x < params$df_pacboard[, params$intervention_total_undiscounted_qalys],
        "lower than undiscounted QALYs",
        "discounted QALYs are {label_check} for the intervention"
      )
    msg_qalys <- paste(msg_qalys,
                       valid_disc_qalys_int$messages$message,
                       sep = "\n")
}
if(params$validation_checks_choice == TRUE &
   params$comparator_total_discounted_qalys != "" &
   params$comparator_total_undiscounted_qalys != "") {
  valid_disc_qalys_comp <- pacheck:::do_check(
        params$df_pacboard,
        params$comparator_total_discounted_qalys,
        ~ .x < params$df_pacboard[, params$comparator_total_undiscounted_qalys],
        "lower than undiscounted QALYs",
        "discounted QALYs are {label_check} for the comparator"
      )
    msg_qalys <- paste(msg_qalys,
                       valid_disc_qalys_comp$messages$message,
                       sep = "\n")
    }
cat(msg_qalys)
```

`r if(params$validation_checks_choice == TRUE & params$intervention_total_discounted_costs != "" & params$comparator_total_discounted_costs != "") {paste("## Outcomes: total discounted costs")}`
```{r validation_t_costs, warning = FALSE}
msg_costs <- c()
if(params$validation_checks_choice == TRUE &
   params$intervention_total_discounted_costs != "" &
   params$comparator_total_discounted_costs != ""
   ) {
  valid_costs_int <- pacheck:::do_check(
    params$df_pacboard,
    params$intervention_total_discounted_costs,
    ~ .x > 0,
    "positive",
    "total discounted costs are {label_check} for the intervention"
  )
  valid_costs_comp <- pacheck:::do_check(
    params$df_pacboard,
    params$comparator_total_discounted_costs,
    ~ .x > 0,
    "positive",
    "total discounted costs are {label_check} for the comparator"
  )
  msg_costs <- paste(valid_costs_int$messages$message,
                     valid_costs_comp$messages$message,
                     sep = "\n")
}
if(params$validation_checks_choice == TRUE &
   params$intervention_total_discounted_costs != "" &
   params$intervention_total_undiscounted_costs != "") {
  valid_disc_costs_int <- pacheck:::do_check(
        params$df_pacboard,
        params$intervention_total_discounted_costs,
        ~ .x < params$df_pacboard[, params$intervention_total_undiscounted_costs],
        "lower than undiscounted costs",
        "discounted costs are {label_check} for the intervention"
      )
    msg_costs <- paste(msg_costs,
                       valid_disc_costs_int$messages$message,
                       sep = "\n")
}
if(params$validation_checks_choice == TRUE &
   params$comparator_total_discounted_costs != "" &
   params$comparator_total_undiscounted_costs != "") {
  valid_disc_costs_comp <- pacheck:::do_check(
        params$df_pacboard,
        params$comparator_total_discounted_costs,
        ~ .x < params$df_pacboard[, params$comparator_total_undiscounted_costs],
        "lower than undiscounted costs",
        "discounted costs are {label_check} for the comparator"
      )
    msg_costs <- paste(msg_costs,
                       valid_disc_costs_comp$messages$message,
                       sep = "\n")
    }
cat(msg_costs)
```

`r if(params$ce_plot_choice == TRUE) {paste("# Cost-effectiveness plane")}`
```{r ce}
if (
  params$ce_plot_choice == TRUE &
  params$intervention_total_discounted_qalys != "" &
  params$intervention_total_discounted_costs != "" &
  params$comparator_total_discounted_qalys != "" &
  params$comparator_total_discounted_costs != ""
) {
  pacheck::plot_ce(
    df = params$df_pacboard,
    e_int = params$intervention_total_discounted_qalys,
    c_int = params$intervention_total_discounted_costs,
    e_comp = params$comparator_total_discounted_qalys,
    c_comp = params$comparator_total_discounted_costs
  )
}
```

`r if(params$ice_plot_choice == TRUE | params$ice_summary_choice == TRUE ) {paste("# Incremental cost-effectiveness plane and summary")}`
```{r ice}
if(params$ice_plot_choice == TRUE &
   params$intervention_total_discounted_qalys != "" &
   params$intervention_total_discounted_costs != "" &
   params$comparator_total_discounted_qalys != "" &
   params$comparator_total_discounted_costs != "") {
  pacheck::plot_ice(df = params$df_pacboard,
                    e_int = params$intervention_total_discounted_qalys,
                    c_int = params$intervention_total_discounted_costs,
                    e_comp = params$comparator_total_discounted_qalys,
                    c_comp = params$comparator_total_discounted_costs,
                    col = if(params$col_ice == "") {NULL} else {params$col_ice},
                    n_it = if(exists("params$n_it_highlight")) {as.numeric(params$n_it_highlight)} else {NULL},
                    wtp = params$wtp_ice
  )
}
  if (params$ice_summary_choice == TRUE &
      params$intervention_total_discounted_qalys != "" &
      params$intervention_total_discounted_costs != "" &
      params$comparator_total_discounted_qalys != "" &
      params$comparator_total_discounted_costs != "") {
    knitr::kable(
      pacheck::summary_ice(
        df = params$df_pacboard,
        e_int = params$intervention_total_discounted_qalys,
        c_int = params$intervention_total_discounted_costs,
        e_comp = params$comparator_total_discounted_qalys,
        c_comp = params$comparator_total_discounted_costs
      ),
      caption = "Proportion of iterations in each quadrant"
    )
  }
```

`r if(params$ceac_plot_choice == TRUE) {paste("# Cost-effectiveness acceptability curve")}`
```{r ceac}
    if (params$ceac_plot_choice == TRUE &
        params$intervention_total_discounted_qalys != "" &&
        params$intervention_total_discounted_costs != "" &&
        params$comparator_total_discounted_qalys != "" &&
        params$comparator_total_discounted_costs != "") {
      ceac_inputs <- pacheck::calculate_ceac(
        df = params$df_pacboard,
        e_int = params$intervention_total_discounted_qalys,
        c_int = params$intervention_total_discounted_costs,
        e_comp = params$comparator_total_discounted_qalys,
        c_comp = params$comparator_total_discounted_costs,
        v_wtp = seq(
          from = params$ceac_min,
          to = params$ceac_max,
          by = params$ceac_step
        )
      )
      pacheck::plot_ceac(df = ceac_inputs,
                         wtp = "WTP_threshold")
    }
```
